% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{\textbf{#1}}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\newcounter{none} % for unnumbered tables
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\section{CS 6120 --- Final Project
Report}\label{cs-6120-final-project-report}

\textbf{Title}: Conference Matching Platform: Hybrid RAG and Semantic
Retrieval\\
\textbf{Authors}: Xian Cao\\
\textbf{Repository}:
\url{https://github.com/xiancao2024/Conference-Matching-Platform}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{1 Objectives and
Introduction}\label{objectives-and-introduction}

The sheer volume of concurrent sessions and attendees at modern
large-scale conferences makes it notoriously difficult for participants
to navigate event schedules and build meaningful professional
connections. This project builds a \textbf{Retrieval-Augmented
Generation (RAG) matching platform} specifically designed to solve the
conference discovery problem.

Using entirely real-world event attendance data, the system successfully
normalizes unstructured attendance logs into a relational schema
containing attendee profiles and event sessions. By heavily indexing
these entities, the platform runs a sophisticated \textbf{hybrid
matching pipeline} combining traditional lexical keyword scoring with
advanced semantic retrieval models (via Sentence Transformers and
FAISS).

The primary objective of this project is to demonstrate a
production-ready, Program-Aided Language (PAL) style assistant that can
natively understand natural language matchmaking queries, surface the
most highly relevant attendees or sessions, and utilize generative LLMs
to synthesize human-readable explanations validating why the system
retrieved those specific results.

\subsection{2 Background and Related
Work}\label{background-and-related-work}

\textbf{Dataset Context}: We rely on the public Kaggle Event Attendance
Dataset (\texttt{cankatsrc/event-attendance-dataset}). This dataset
provides a robust challenge because it consists of raw attendance CSV
logs---capturing interactions rather than clean profiles. It contains
fields such as \emph{Event ID, Event Name, Location, Date \& Time,
Attendee Name, Attendee Email,} and \emph{Attendee Phone}. This dataset
accurately mirrors the messy telemetry data corporate event organizers
often possess, making it highly suitable for an end-to-end normalization
and retrieval task.

\textbf{Related Work}: Modern open-domain QA heavily utilizes the
Retrieval-Augmented Generation paradigm (Lewis et al., 2020; Karpukhin
et al., 2020). However, traditional RAG focuses solely on retrieving
text chunks to answer trivia or summarize documents. This project
extends RAG principles into the domain of \textbf{Program-Aided Language
models (PAL)} and \textbf{Recommendation Systems}. Rather than
retrieving static paragraphs, the LLM orchestrates over a structured
database of people and events, blending dense vector retrieval with
deterministic attribute filtering.

\subsection{3 Approach and
Implementation}\label{approach-and-implementation}

\subsubsection{System Architecture
Overview}\label{system-architecture-overview}

The platform was built following a robust three-stage data and retrieval
pipeline: 1. \textbf{Data Ingestion \& Normalization}: The raw
attendance rows are parsed and heuristically structured into a
JSON-based conference schema. 2. \textbf{Hybrid Retrieval Engine}: A
matcher combining BM25-style lexical keyword scoring and dense vector
similarity embedding-backed by FAISS. 3. \textbf{Generative UI layer}: A
web UI and programmatic agent that interprets user queries, executes the
hybrid matcher, and generates contextual explanations using a locally
hosted LLM (Ollama).

\subsubsection{Engineering Design
Decisions}\label{engineering-design-decisions}

\begin{itemize}
\tightlist
\item
  \textbf{Conservative Heuristic Normalization}: Since the CSV only
  contains emails and event names, we derive organization profiles
  heuristically from the email domain (filtering out generic providers
  like gmail.com). We further derive topical ``sectors'' via custom
  phrase and token mapping over the event titles.
\item
  \textbf{Hybrid Ranking Strategy}: Lexical token matching is excellent
  for specific names (e.g., ``John Doe''), while semantic embedding
  matching (using \texttt{all-MiniLM-L6-v2}) is critical for conceptual
  queries (e.g., ``AI and climate change''). We harmoniously combine
  keyword overlap, concept matching, and structured filtering to compute
  a joint relevance score.
\item
  \textbf{Explainability}: Instead of simply returning a list of links,
  the platform uses an LLM (Llama 3) to rerank the top candidates and
  append a one-sentence natural language rationale for the match,
  increasing user trust.
\end{itemize}

\subsubsection{Code Organization}\label{code-organization}

\begin{itemize}
\tightlist
\item
  \texttt{conference\_matching/kaggle\_import.py} --- The ETL pipeline
  bridging Kaggle CSVs directly to our structured JSON schema.
\item
  \texttt{conference\_matching/engine.py} --- Implements the lexical
  parsing, FAISS vector indexing, and hybrid ranker scoring functions.
\item
  \texttt{conference\_matching/llm.py} --- Handles the prompt
  engineering and structured JSON parsing to communicate with the local
  LLM.
\end{itemize}

\subsection{4 Data and Data Analysis}\label{data-and-data-analysis}

\textbf{Data Source}: - Kaggle Dataset URI:
\url{https://www.kaggle.com/datasets/cankatsrc/event-attendance-dataset}

\textbf{Exploratory Data Analysis}: Through our import scripts, we
normalize the raw tabular graph into unique entities. Our system
automatically aggregates attendance counts to identify the most heavily
trafficked event sessions, enabling popularity-based boosting during
retrieval. We also clean edge-case variations in CSV column headers
using hardcoded alias mapping logic in \texttt{data.py} to ensure high
data integrity even if the upstream Kaggle dataset schema drifts.

\subsection{5 Results and Evaluation}\label{results-and-evaluation}

\subsubsection{Evaluation Methodology}\label{evaluation-methodology}

Without manually labeled ``perfect'' recommendations for every query, we
pioneered a \textbf{weak-label evaluation harness}. For each imported
attendee, their known, historical session registrations are defined as
the ground-truth ``relevant'' search items. We then simulate search
queries on their behalf and measure whether our engine can retrieve the
sessions they actually chose to attend. We compare our proposed Hybrid
Matcher against a baseline Keyword-Only lexical matcher.

\subsubsection{Quantitative Results}\label{quantitative-results}

\emph{(Based on a weak-label evaluation benchmark spanning 3 distinct
query types)}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2286}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2571}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.3143}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Metric
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Hybrid Matcher
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Keyword Baseline
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Relative Improvement
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Precision@5 & 0.20 & 0.20 & 0\% \\
Recall@5 & 1.00 & 1.00 & 0\% \\
\textbf{nDCG@5} & \textbf{1.00} & 0.54 & \textbf{+85\%} \\
\textbf{MRR} & \textbf{1.00} & 0.39 & \textbf{+156\%} \\
\end{longtable}
}

\subsubsection{Analytical Narrative}\label{analytical-narrative}

Both systems naturally achieve a high Recall@5 because the dataset is
constrained, meaning both engines successfully surface the relevant
session \emph{somewhere} in the top 5 results.

However, the ranking quality represents a massive leap forward. The
hybrid system (utilizing Sentence Transformers via HuggingFace and
FAISS) achieves perfect nDCG@5 and Mean Reciprocal Rank (MRR)---which
means \textbf{it ranks the single correct session at position \#1 for
every single query evaluated}.

The keyword-only baseline suffers from semantic mismatch (e.g., failing
to connect the query ``machine learning'' to a session titled ``Neural
Networks''), dragging its MRR down to 0.39. The hybrid approach's 156\%
relative improvement directly proves that blending dense embeddings with
lexical keyword overlap is critical for high-fidelity conference
matchmaking.

\subsection{6 Conclusions and Future
Work}\label{conclusions-and-future-work}

This implementation decisively proves that raw, flat attendance records
can be systematically normalized into a rich entity graph suitable for
state-of-the-art hybrid vector retrieval and RAG-driven orchestrations.
The platform is highly practical for small-to-medium conferences, and
serves as an excellent foundation for professional networking tools.

\textbf{Future Directions}: 1. \textbf{Profile Enrichment}:
Automatically query external APIs (LinkedIn, Twitter) to scrape and
enrich attendee profiles with their actual Job Titles, Companies, and
self-authored biographies. 2. \textbf{Bidirectional Matchmaking}:
Upgrade the system beyond search to become a proactive recommendation
engine that actively proposes mutual double-opt-in meetings between
attendees with complementary ``Asks'' and ``Offers''. 3.
\textbf{Multi-Agent PAL}: Integrate multiple specialized LLM agents
(e.g., an LLM specialized in scheduling, and an LLM specialized in
introductory email drafting) routing through LangChain to automate the
entire meeting arrangement lifecycle.

\subsection{7 Submission Guidelines}\label{submission-guidelines}

\begin{itemize}
\tightlist
\item
  \textbf{PDF file}: Included in the submission materials.
\item
  \textbf{GCP Endpoint}: \url{http://34.169.130.58:8000}
\item
  \textbf{Github URL}:
  \url{https://github.com/xiancao2024/Conference-Matching-Platform}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{Appendix: How to reproduce
locally}\label{appendix-how-to-reproduce-locally}

\textbf{1. Create virtual environment and install dependencies}

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{python3} \AttributeTok{{-}m}\NormalTok{ venv .venv}
\ExtensionTok{.venv/bin/python} \AttributeTok{{-}m}\NormalTok{ pip install }\AttributeTok{{-}r}\NormalTok{ requirements.txt}
\end{Highlighting}
\end{Shaded}

\textbf{2. Import the Kaggle dataset directly via Kagglehub}

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{pip}\NormalTok{ install kagglehub}
\ExtensionTok{python3} \AttributeTok{{-}m}\NormalTok{ conference\_matching.kaggle\_import}
\end{Highlighting}
\end{Shaded}

\textbf{3. Start the Server}

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{python3}\NormalTok{ server.py}
\end{Highlighting}
\end{Shaded}

\textbf{4. Run complete evaluation suite}

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{python3} \AttributeTok{{-}m}\NormalTok{ conference\_matching.evaluation}
\end{Highlighting}
\end{Shaded}


\end{document}
